VISUALIZATION OF THE RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL

### 2019-09-20 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
started fleshing out Cavalieri section

 \begin{definition}\label{Def3}
Text of Definition~\ref{Def3}.
 \end{definition}

@@

@@

\noindent
Note that $g = h^{-1}$ per definition. Moreover $g$ is guaranteed to exist, since $h$ is bijective.

\begin{definition}\label{def:cav_integral}
Define a partition $\mathcal{P}_1$ of $[a,b]$ to be a set of points $x_0^1, x_1^1,\cdots,x_n^1$, 
where $a = x_0^1 \leq x_1^1 \leq \cdots \leq x_n^1 = b$. For each partition 
$\mathcal{P}_1$ of $[a,b]$ write $\Delta x_k^1 = x_k^1-x_{k-1}^1$. 
%Since both boundaries of any integration strip are necessarily
%translations of the translational function $a(y)$, we can apply the transformation
%function $h$ to the partition $\mathcal{P}_1$. 
If the transformation function $h$ is strictly increasing,
the application of $h$ to the partition $\mathcal{P}_1$ induces a new partition $\mathcal{P}_2 = \{x_0^2, x_1^2,\cdots, x_n^2\}$.
Otherwise, if $h$ is strictly decreasing, the application of $h$ induces a reversed partition $\mathcal{P}_2 = \{x_n^2, \cdots, x_1^2,x_0^2\}$. It
can be assumed that $h$ is strictly increasing, without any loss of generality.  Let 
$M_k = \sup \{f (x), h(x_{i-1}^1) = x_{i-1}^2 \leq x \leq x_i^2 = h(x_i^1)\}$, $m_k = \inf \{f (x), h(x_{i-1}^1) = x_{i-1}^2 \leq x \leq x_i^2 = h(x_i^1)\}$, and set 
\begin{equation}
\label{eq:c_up}
\mathcal{C}_U(\mathcal{P}_1,f,h) = \sum_{k=1}^n M_k \Delta x_k, 
\end{equation}
and
\begin{equation}
\label{eq:c_low}
\mathcal{C}_L(\mathcal{P}_1,f,h) = \sum_{k=1}^n m_k \Delta x_k. 
\end{equation}
The sums in Eq.~\eqref{eq:c_up} and Eq.~\eqref{eq:c_low} are respectively called the the upper and lower Cavalieri sums.
If there is a unique number $I$ that satisfies the inequality $\mathcal{C}_L(\mathcal{P}_1,f,h)\leq I \leq \mathcal{C}_U(\mathcal{P}_1,f,h)$ for all 
partitions $\mathcal{P}_1$ of $[a,b]$, then $I$ is called the Cavalieri integral of $f$ from $a(y)$ to $b(y)$ and is denoted by
\begin{equation}
\int_{a(y)}^{b(y)} f(x) dx.
\end{equation}
\end{definition}

>>>>

Ackerman et al. used the notion of non-rectangular integration strips to define the so called Cavalieri integral. The area of a non-rectangular 
integration strip is calculated using Cavalieri's principle. The formal definition of the Cavalieri integral is given in Definition~\ref{def:cav_integral}.
It is, however, our experience that Definition~\ref{def:cav_integral} is hard to assimilate if it is encounterd by a reader for the first time. We, therefore, encourage 
readers who are not familiar with the Cavalieri integral to rather first read Section~\ref{??} instead. The reader should only refer back to the definitions 
presented in this sections when things in Section~\ref{??} become unclear. Moreover, the definitions presented below were taken from [?]. Furthermore, none of the theorems in this sections are proved, the proofs are contained in [].

@@

Let $a(y)$ be a translational function with respect to a real--valued function $f(x)$ on the interval $[a,b]$. Moreover, $b(y) = a(y) + (b-a)$. Furthermore, the functions $a(y)$ and $b(y)$ intersect $f(x)$ at $a'$ and $b'$ respectively.
These assertions are assumed to be true throughout the paper and will not be repeated again.

@@

\begin{theorem}
The mapping $g(x)$ is a strictly monotone continious function. The function $g(x)$ is, therefore, invertable.
\end{theorem}

\begin{theorem}
The function $g(x)$ is equal to $h^{-1}(x)$.
\end{theorem}

The function $g(x)$ is known as the inverse transformation function.

\begin{definition}\label{def:cav_integral}
Define a partition $\mathcal{P}_1$ of $[a,b]$ to be a set of points $x_0^1, x_1^1,\cdots,x_n^1$, 
where $a = x_0^1 \leq x_1^1 \leq \cdots \leq x_n^1 = b$. For each partition 
$\mathcal{P}_1$ of $[a,b]$ write $\Delta x_k^1 = x_k^1-x_{k-1}^1$. 
%Since both boundaries of any integration strip are necessarily
%translations of the translational function $a(y)$, we can apply the transformation
%function $h$ to the partition $\mathcal{P}_1$. 
If the transformation function $h$ is strictly increasing,
the application of $h$ to the partition $\mathcal{P}_1$ induces a new partition $\mathcal{P}_2 = \{x_0^2, x_1^2,\cdots, x_n^2\}$.
Otherwise, if $h$ is strictly decreasing, the application of $h$ induces a reversed partition $\mathcal{P}_2 = \{x_n^2, \cdots, x_1^2,x_0^2\}$. It
can be assumed that $h$ is strictly increasing, without any loss of generality.  Let 
$M_k = \sup \{f (x), h(x_{i-1}^1) = x_{i-1}^2 \leq x \leq x_i^2 = h(x_i^1)\}$, $m_k = \inf \{f (x), h(x_{i-1}^1) = x_{i-1}^2 \leq x \leq x_i^2 = h(x_i^1)\}$, and set 
\begin{equation}
\label{eq:c_up}
\mathcal{C}_U(\mathcal{P}_1,f,h) = \sum_{k=1}^n M_k \Delta x_k^1, 
\end{equation}
and
\begin{equation}
\label{eq:c_low}
\mathcal{C}_L(\mathcal{P}_1,f,h) = \sum_{k=1}^n m_k \Delta x_k^1. 
\end{equation}
The sums in Eq.~\eqref{eq:c_up} and Eq.~\eqref{eq:c_low} are respectively called the the upper and lower Cavalieri sums.
If there is a unique number $I$ that satisfies the inequality $\mathcal{C}_L(\mathcal{P}_1,f,h)\leq I \leq \mathcal{C}_U(\mathcal{P}_1,f,h)$ for all 
partitions $\mathcal{P}_1$ of $[a,b]$, then $I$ is called the Cavalieri integral of $f$ from $a(y)$ to $b(y)$ and is denoted by
\begin{equation}
\int_{a(y)}^{b(y)} f(x) dx.
\end{equation}
\end{definition}
